Untitled

### 2021-09-19 2021_realloc/test.Rmd
correction estimation model
slight mistake in the expression of the moments

@@

```{r include=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(purrr)
```

@@

@@

\begin{align*}
Var(C_i Z_i) & = E( C_i^2 Z_i^2 ) - E(C_i Z_i)^2,\\
& =  E( C_i^2) E(Z_i^2 ) -E(C_i)^2 E(Z_i)^2,\\
& = p_i E(Z_i^2 ) - p_i^2 E(Z_i)^2 = p_i ( Var(Z_i) + (1-p_i) E(Z_i)^2),\\
& = p_i\left( \frac{\mu(x_i)^2 }{(1-p_i)^2} (e^{\sigma^2}-1) + (1-p_i) \frac{\mu(x_i)^2 }{(1-p_i)^2}\right),\\
& = \frac{p_i}{(1-p_i)^2} \mu(x_i)^2  \left(e^{\sigma^2} -p_i \right)  
\end{align*}

>>>>

---
title: "Untitled"
author: "Baptiste Alglave"
date: "15/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
```

@@

## Fitting a Delta Log normal distribution for the catch

Recals that at the VMS ping level $Y_i = C_i Z_i, $

with

$$C_i \sim  mathcal{B}(p_i), \quad p_i = $$

### the probability of an empty catch

@@

\begin{align*}
Var(C_i Z_i) & = E( C_i^2 Z_i^2 ) - E(C_i Z_i)^2,\\
& =  E( C_i^2) E(Z_i^2 ) -E(C_i)^2 E(Z_i)^2,\\
& = (1- p_i) E(Z_i^2 ) - (1-p_i)^2 E(Z_i)^2 = (1-p_i) ( Var(Z_i)  + p_i E(Z_i)^2),\\
& = (1-p_i)\left( \mu(x_i)^2 (e^{\sigma^2}-1) + p_i \mu(x_i)^2 \right),\\
& = (1-p_i) \mu(x_i)^2 \left ( e^{\sigma^2}-1  + p_i \right),\\
\end{align*}
